Rapid evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-08-18 ms.Rmd
Added new figures for Devi's new analysis. abs JND by body region and population for chromatic and luminance

# Fit model testing this idea above
  Diff_dL <- lmer(dL_diff_abs ~ SVL + Population + (1|ID), data=Diff)
  summary(Diff_dL)

@@

# Refit mdoel using robust standard errors
  robust_Diff_dl <- clubSandwich::conf_int(Diff_dL, cluster = Diff$ID, vcov =  "CR2")

# Wald tests - Test significance of pop dofferences and SVL differences averaging over body regions
   robust_Diff_dl_pop <- Wald_test(Diff_dL, constraints = constrain_zero(3), 
                                  cluster = Diff$ID, vcov = "CR2")
   robust_Diff_dl_svl <- Wald_test(Diff_dL, constraints = constrain_zero(2), 
                                  cluster = Diff$ID, vcov = "CR2")

##################
# Chromatic contrast
##################  
   # Fit model testing this idea above
  Diff_dS <- lmer(dS_diff_abs ~  SVL + Population + (1|ID), data=Diff)
  summary(Diff_dS)

@@

# Current Sec
To gauge the extent of color plasticity, we examined individual change between display (male-male contest) and anti-predator (bird) color states (absolute difference in JNDs between states; N = `r N_diff[1,2]` Hawaii, N = `r N_diff[2,2]` Kenya).

Together, these results indicate that chameleons introduced to Hawaii only 50 years ago have evolved signals that are locally adapted, more conspicuous to conspecifics, and show greater changes between display and anti-predator color states. While it is possible that differences between Hawaiian and Kenyan chameleons could reflect a founder effect, the observed differences are all in the predicted direction of adaptive change, whereas founder effects are expected to be random with respect to the local environment.

@@

>>>>

# Fit model testing this idea above. First just test for body region interaction. But, needs RVE
    Diff_dL_BR_int <- lmer(dL_diff_abs ~ sc_SVL + Population + BodyRegion + BodyRegion:Population + (1|ID), data=Diff)
    summary(Diff_dL_BR_int)

    # Significance of interaction
      robust_Diff_dl_int <- Wald_test(Diff_dL_BR_int, constraints = constrain_zero(7:9), 
                                    cluster = Diff$ID, vcov = "CR2")
# Main effects BR
    Diff_dL_BR_me <- lmer(dL_diff_abs ~ sc_SVL + Population + BodyRegion  + (1|ID), data=Diff)
    summary(Diff_dL_BR_me)

    # Sig of Body Region
        robust_Diff_dL_BR_me <- Wald_test(Diff_dL_BR_me, constraints = constrain_zero(4:6), 
                                    cluster = Diff$ID, vcov = "CR2")

# Then fit marginalised model so that body regions are averaged
  Diff_dL <- lmer(dL_diff_abs ~ sc_SVL + Population + (1|ID), data=Diff)
  summary(Diff_dL)

@@

# Refit mdoel using robust standard errors
  robust_Diff_dl_BR <- clubSandwich::conf_int(Diff_dL, cluster = Diff$ID, vcov =  "CR2")

# Wald tests - Test significance of pop dofferences and SVL differences averaging over body regions

  robust_Diff_dl_pop <- Wald_test(Diff_dL, constraints = constrain_zero(3), 
                                  cluster = Diff$ID, vcov = "CR2")
   robust_Diff_dl_svl <- Wald_test(Diff_dL, constraints = constrain_zero(2), 
                                  cluster = Diff$ID, vcov = "CR2")

##################
# Chromatic contrast
##################

  # Fit model testing this idea above. First just test for body region interaction. But, needs RVE
    Diff_dS_BR_int <- lmer(dS_diff_abs ~ sc_SVL + Population + BodyRegion + BodyRegion:Population + (1|ID), data=Diff)
    summary(Diff_dS_BR_int)

    # Significance of interaction
      robust_Diff_dS_int <- Wald_test(Diff_dS_BR_int, constraints = constrain_zero(7:9), 
                                    cluster = Diff$ID, vcov = "CR2")
  # Main effects BR
    Diff_dS_BR_me <- lmer(dS_diff_abs ~ sc_SVL + Population + BodyRegion  + (1|ID), data=Diff)
    summary(Diff_dS_BR_me)

    # Sig of Body Region
      robust_Diff_dS_BR_me <- Wald_test(Diff_dS_BR_me, constraints = constrain_zero(4:6), 
                                    cluster = Diff$ID, vcov = "CR2")

# Fit model testing this idea above
  Diff_dS <- lmer(dS_diff_abs ~  SVL + Population + (1|ID), data=Diff)
  summary(Diff_dS)

@@

To gauge the extent of color plasticity, we examined individual change between display (male-male contest) and anti-predator (bird) color states (absolute difference in JNDs between states; N = `r N_diff[1,2]` Hawaii, N = `r N_diff[2,2]` Kenya). While body regions varied in there overall effects (significant body region effect: chromatic: $F_{`r robust_Diff_dS_BR_me$df_num`,`r robust_Diff_dS_BR_me$df_denom`}$ = `r robust_Diff_dS_BR_me$Fstat`, p = `r p_value(robust_Diff_dS_BR_me[,6])`; lunminance: $F_{`r robust_Diff_dL_BR_me$df_num`,`r robust_Diff_dL_BR_me$df_denom`}$ = `r robust_Diff_dL_BR_me$Fstat`, p = `r p_value(robust_Diff_dL_BR_me[,6])`, but no population by bodyregion interaction: chromatic: $F_{`r robust_Diff_dS_int$df_num`,`r robust_Diff_dS_int$df_denom`}$ = `r robust_Diff_dS_int$Fstat`, p = `r p_value(robust_Diff_dS_int[,6])`; lunminance: $F_{`r robust_Diff_dl_int$df_num`,`r robust_Diff_dl_int$df_denom`}$ = `r robust_Diff_dl_int$Fstat`, p = `r p_value(robust_Diff_dl_int[,6])`) all exhibited positive absolute JND's between display and antipreadtor color states. Overall, Hawaiian chameleons showed greater chromatic but not luminance change (chromatic: $F_{`r robust_Diff_dS_pop$df_num`,`r robust_Diff_dS_pop$df_denom`}$ = `r robust_Diff_dS_pop$Fstat`, p = `r p_value(robust_Diff_dS_pop[,6])`; luminance: $F_{`r robust_Diff_dl_pop$df_num`,`r robust_Diff_dl_pop$df_denom`}$ = `r robust_Diff_dl_pop$Fstat`, p = `r p_value(robust_Diff_dl_pop[,6])`). Together, these results indicate that chameleons introduced to Hawaii only 50 years ago have evolved signals that are locally adapted, more conspicuous to conspecifics, and show greater changes between display and anti-predator color states. While it is possible that differences between Hawaiian and Kenyan chameleons could reflect a founder effect, the observed differences are all in the predicted direction of adaptive change, whereas founder effects are expected to be random with respect to the local environment.

@@

```{r}
# Courship data

##########
# Data
##########
abs_display_pred <- Diff %>%
                group_by(Population, BodyRegion) %>%
                summarise( Mean_dS_abs = mean(dS_diff_abs, na.rm = T), 
                             SE_dS_abs = sd(dS_diff_abs)/sqrt(length(unique(ID))),
                             Upper_dS_abs = Mean_dS_abs + 1.96*SE_dS_abs,
                             Lower_dS_abs = Mean_dS_abs - 1.96*SE_dS_abs, 
                           Mean_dL_abs = mean(dL_diff_abs, na.rm = T), 
                             SE_dL_abs = sd(dL_diff_abs)/sqrt(length(unique(ID))),
                             Upper_dL_abs = Mean_dL_abs + 1.96*SE_dL_abs,
                             Lower_dL_abs = Mean_dL_abs - 1.96*SE_dL_abs) %>% as.data.frame()

##########
# Plots
##########

#plots
p1 <- ggplot(abs_display_pred, aes(x = Population, y = Mean_dS_abs, color = BodyRegion, group = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dS_abs, ymax = Upper_dS_abs), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("Population") + 
  ylab("Chromatic contrast (JND)") +
  theme_bw() +
  labs(colour = "Body Region") +
  theme(legend.position = "none",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

p2 <- ggplot(abs_display_pred, aes(x = Population, y = Mean_dL_abs, color = BodyRegion, group = BodyRegion)) +
  geom_point(size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymin = Lower_dL_abs, ymax = Upper_dL_abs), position = position_dodge(width=0.5), width = 0) + 
  geom_line(position = position_dodge(width=0.5)) + 
  scale_color_manual(values = wes_palette("Cavalcanti1")) + #Change color palette here see: https://github.com/karthik/wesanderson
  xlab("Population") + 
  ylab("Luminance contrast (JND)") +
  theme_bw() +
  labs(colour = "Body Region") +
  theme(legend.position = "right",
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text=element_text(size=18),
    axis.title=element_text(size=20,face="bold"),
    legend.text =element_text(size = 12),
    legend.title =element_text(size = 12, face = "bold"))

#pdf(file="./output/figures/Figure2.pdf", height = 10, width = 18)
plot_grid(p1, p2, labels = c("A", "B"), label_size = 30,
  label_fontface = "bold", rel_widths=c(1,1))
```
